FinalManuscript_DISCS_UG

### 2018-07-14 parts/01_introduction_01contextofstudy.tex
Revisions to Ch1

Digital data privacy and security is a growing concern in various fields, such as  cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys. a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel:  and thus much research has been done on the development and application of various cryptosystems.

One such particular application of cryptography is image encryption. While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images \cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed \cite{murugan_survey_2018}.

However, research has also considered a type of cryptosystem, homomorphic cryptosystems, where in addition to allowing the secure transmission of data, it is also possible to perform computations with encrypted data, the most basic of which being addition and multiplication. Numerous homomorphic cryptosystems exist, which allow for data to be manipulated without compromising data privacy \cite{fontaine_survey_2007, sen_homomorphic_2013}. In homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations \cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.

>>>>

Digital data privacy and security is a growing concern in various fields, such as cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys, and has an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key \cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel. Much research has been done on the development and application of various cryptosystems.

One particular application of cryptography is image encryption. While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images \cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed \cite{murugan_survey_2018}.

However, research has also considered homomorphic cryptosystems, which not only allow the secure transmission of data, but also allow computations with encrypted data. In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data. These operations are then preserved when the data is decrypted. In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure \cite{fontaine_survey_2007, sen_homomorphic_2013}. While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations \cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.

### 2018-07-14 parts/01_introduction_02researchquestions.tex
Revisions to Ch1

In this study, we ask

\begin{enumerate}
    \item Research questions 1...
    \item Research questions 2...
    \item Research questions 3...
\end{enumerate}

>>>>

By implementing homomorphic cryptosystems and creating an OpenCV library so they can be easily used, we aim to address our main research question: What is the best method for image data to be encrypted and manipulated for practical applications?

More specifically, our research will address the following sub-research questions:
\begin{enumerate}
	\item Which homomorphic cryptosystems admit more image processing operations?
	\item Which homomorphic cryptosystems are the most time-efficient in applying image processing operations?
	\item Which homomorphic cryptosystems are the most secure under differential and entropy attacks?
\end{enumerate}

### 2018-07-14 parts/01_introduction_03objectives.tex
Revisions to Ch1

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et. al. \cite{li_elliptic_2012}, and the fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}. Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
Furthermore, one of the main problems in homomorphic encryption is the practicality of homomorphic encryption schemes. Homomorphic cryptosystems are known to be slower compared to other cryptosystems \cite{sen_homomorphic_2013}.
Taking the above into account, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit more image processing operations;
		\item Compare the security of common image processing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
    \item Compare the efficiency of common image processsing operations under known homomorphic encryption schemes;
    \item Create a library for OpenCV to allow for convenient use and comparison of these homomorphic encryption schemes.
\end{enumerate}

>>>>

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic cryptosystem, we believe this study can be extended by considering other known homomorphic encryption schemes, such as those found in \cite{li_elliptic_2012, hutchison_fully_2010}. Our study aims to provide an objective comparison of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.

Our main research objective is to assess the practicality of various homomorphic cryptosystems in image encryption. Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time \cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed \cite{li_elliptic_2012}. Finally, as data security is the primary purpose of cryptosystems, we want to evaluate the security of homomorphic cryptosystems as image encryption schemes.

In summary, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processing operations, in other words, determine which schemes admit more image processing operations;
		\item Compare the security of common image processing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
    \item Compare the time efficiency of common image processing operations under known homomorphic encryption schemes;
    \item Create a library for OpenCV to allow for convenient use and comparison of these homomorphic encryption schemes.
\end{enumerate}

### 2018-07-14 parts/01_introduction_04significanceofstudy.tex
Revisions to Ch1

The results of the study will provide

>>>>

This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption \cite{sen_homomorphic_2013}. The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplicaiton) on encrypted data, however, for homomorphic cryptosystems to be useful for practical image processing applications, support for more complicated operations such as image convolution must be demonstrated as well. While implementations of homomorphic encryption algorithms exist \cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets algorithms for which statistical tests have not been performed for image processing operations.

We wish to contribute to existing models for the secure transmission and modification of image data by developing a library which allows the use and comparison of various homomorphic encryption algorithms.  Examples include applications in cloud storage \cite{potey_homomorphic_2016} and video surveillance \cite{upmanyu_efficient_2009}. This allows service providers to perform image manipulation for clients without compromising data privacy.
